Lasso_RCI_Response

### 2024-05-13 Lasso_RCI_Response.Rmd
Act variables = insignificant models?

## Read in the dataset. 
```{r}
Mothership1 <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
#DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
Mothership1

list.files("~/Desktop/Coding/data/ACT_scores")
# path = "~/Desktop/Coding/data/ACT_scores"
# # 
# length(dir(path))
# for(i in dir(path))
# {
#   df_1 <- read_sav(paste0(path,"/",i))
#   Mothership_mindful <- left_join(Mothership1,df_1, by = join_by(ID1 == ID1))
# }

df_1 <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPost_1.sav")
Mothership1 <- left_join(Mothership1,df_1, by = join_by(ID1 == ID1))
df_2 <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPre_1.sav")
Mothership1 <- left_join(Mothership1,df_2, by = join_by(ID1 == ID1))
df_3 <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_1.sav")
Mothership1 <- left_join(Mothership1,df_3, by = join_by(ID1 == ID1))
df_4 <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_4250-4350.sav")
Mothership1 <- left_join(Mothership1,df_4, by = join_by(ID1 == ID1))
df_5 <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPre_1.sav")
Mothership1 <- left_join(Mothership1,df_5, by = join_by(ID1 == ID1))

view(Mothership_mindful)
```

@@

@@

@@

Mothership_lasso <- Mothership_post |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  #!is.na(Anxiety_Responder),
  ) |>
  select( c(
    ID1,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, CUDOS_pre, CUDOS_post,
  ))
Mothership_lasso_1 <- na.omit(Mothership_lasso)

@@

```{r}
### Anxeity 
Mothership_lasso_anx <- Mothership_post_anx |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  !is.na(Anxiety_Responder),
  CUXOS_pre >= 20,
  ) |>
  select( c(
    ID1,Anxiety_Responder,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC
  ))
Mothership_lasso_anx <- na.omit(Mothership_lasso_anx)

### depression
Mothership_lasso_dep <- Mothership_post_dep |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Depression_Responder),
    CUDOS_pre >= 20,
  ) |>
  select( c(
    ID1, Depression_Responder,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC
  ))
Mothership_lasso_dep <- na.omit(Mothership_lasso_dep)

@@

Vars_dep <- Mothership_lasso_dep |>
  select( c(
    Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, 
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, 
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, #Substance_D, #Psychotic_D,  
    Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre,
    # RDQ
    rdqPOST_coping:rdqPOST_wbs
  ))

@@

```{r}
# min model
glm_min_dep <-
          glm(
    #Outcome varaible
      Depression_Responder ~
    # predictors
      Age_1  + Some_College + Married + IPT_track_1 +
      Days_complete_1 + Days_not_attended_1 + Anxiety_D + Trauma_D +
      Trauma_C + Substance_C +
      rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
    #data
      data = Vars_dep,
    # type of regression : logistic = binary / binomial
      family = "binomial",
    )

# install.packages("rempsyc")
# library(rempsyc)
# nice_table(tidy.summary.min.dep)

@@

# R^2 values  
   R2.min.dep <- performance::r2(glm_min_dep)
  R2.min.dep
# df for Forrest plots
FP.min.dep <- data.frame(cbind(
  Variable = tidy.summary.min.dep$term[2:length(tidy.summary.min.dep$term)],
  OR = OR.min.dep [2:length(OR.min.dep)],
  OR_low  = CI.min.dep [2:length(CI.min.dep$X2.5..),1],
  OR_high = CI.min.dep [2:length(CI.min.dep$X97.5..),2],
  p.values = p.values.min.dep $X2[2:length(p.values.min.dep$X2)]
                    ))

@@

Vars_anx <- Mothership_lasso_anx |>
  select( c(
    Anxiety_Responder,
    # Demographics
    Age_1,Some_College:Married,White, 
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, 
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs
  ))

@@

## min model
  glm_min_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
        Age_1 + Married + Days_complete_1 + 
        Days_not_attended_1 + Anxiety_D + Trauma_D +
        Other + Mood_C + BPD_Co_C + 
        Substance_C + CUXOS_pre +  rdqPOST_coping + 
        rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")

@@

#wald
   library(aod)
   wald.test(b = coef(glm_min_anx),Sigma = vcov(glm_min_anx),Terms= 2:15)

@@

#Change the names of variables
FP_anx$Variable = c("Age", "Unmarried", "Days Completed", 
                    "Days Not Attended", "Anixety Disorder","Trauma Disorder", 
                    "Other Disorder", "Co-Mood Disorder",  "Co-BPD", 
                    "Co-SUD", "CUXOS Pre", "Post Coping", 
                    "Post PMH", "Post Functioning", "Post Wellbeing")

@@

FP_dep <- read_csv("~/Downloads/FP.1se.dep")

@@

FP_dep$Variable = c(
                     "Days Not Attended",
                    "Post Coping", 
                    "Post PMH", "Post Functioning", "Post Wellbeing")

>>>>

## Read in the dataset. 
```{r}
Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
#DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
```

@@

AAQIIpre <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPre_1.sav")
AAQIIpre <- AAQIIpre |>
  mutate(
    AAQIIpre = AAQIIpre_1_1 + AAQIIpre_2_1 + AAQIIpre_3_1 + AAQIIpre_4_1 + 
      AAQIIpre_5_1 + AAQIIpre_6_1 + AAQIIpre_7_1
  )
Mothership <- left_join(Mothership,AAQIIpre, by = join_by(ID1 == ID1))
AAQII

AAQIIpost <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPost_1.sav")
AAQIIpost <- AAQIIpost |>
  mutate(
    AAQIIpost = AAQIIpost_1_1 + AAQIIpost_2_1 + AAQIIpost_3_1 + AAQIIpost_4_1 + 
      AAQIIpost_5_1 + AAQIIpost_6_1 + AAQIIpost_7_1
  )
Mothership <- left_join(Mothership,AAQIIpost, by = join_by(ID1 == ID1))

FMMQ_pre <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPre_1.sav")
FMMQ_pre <- FMMQ_pre|>
  mutate(
    #reverse code items
    FFMQpre_4R  = 6 - FFMQpre_4_1,
    FFMQpre_5R  = 6 - FFMQpre_5_1,  
    FFMQpre_7R  = 6 - FFMQpre_7_1, 
    FFMQpre_8R  = 6 - FFMQpre_8_1, 
    FFMQpre_11R = 6 - FFMQpre_11_1, 
    FFMQpre_12R = 6 - FFMQpre_12_1,
    FFMQpre_14R = 6 - FFMQpre_14_1,
    FFMQpre_17R = 6 - FFMQpre_17_1,
    FFMQpre_19R = 6 - FFMQpre_19_1,
    FFMQpre_22R = 6 - FFMQpre_22_1,
    FFMQpre_23R = 6 - FFMQpre_23_1,
    FFMQpre_24R = 6 - FFMQpre_24_1,
    #create scales
    Desc_Ex_pre =
        FFMQpre_1_1 + FFMQpre_2_1 + FFMQpre_5R + FFMQpre_11R + FFMQpre_16_1,
    Non_react_pre = 
        FFMQpre_3_1 + FFMQpre_9_1 + FFMQpre_13_1 + FFMQpre_18_1 + FFMQpre_21_1,
    Observe_inner_pre = 
        FFMQpre_6_1 + FFMQpre_10_1 + FFMQpre_15_1 + FFMQpre_20_1,
    Self_compasion_pre = 
        FFMQpre_4R + FFMQpre_7R + FFMQpre_14R + FFMQpre_19R + FFMQpre_24R,
    Acting_mindful_pre = 
        FFMQpre_8R + FFMQpre_12R + FFMQpre_17R + FFMQpre_22R + FFMQpre_23R,
    FFMQ_pre_total = 
        Desc_Ex_pre + Non_react_pre + Observe_inner_pre+ Self_compasion_pre + Acting_mindful_pre
    )
Mothership <- left_join(Mothership,FMMQ_pre, by = join_by(ID1 == ID1))

FMMQ_post <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_1.sav")
FMMQ_post <- FMMQ_post|>
  mutate(
    #reverse code items
    FFMQpost_4R  = 6 - FFMQpost_4_1,
    FFMQpost_5R  = 6 - FFMQpost_5_1,  
    FFMQpost_7R  = 6 - FFMQpost_7_1, 
    FFMQpost_8R  = 6 - FFMQpost_8_1, 
    FFMQpost_11R = 6 - FFMQpost_11_1, 
    FFMQpost_12R = 6 - FFMQpost_12_1,
    FFMQpost_14R = 6 - FFMQpost_14_1,
    FFMQpost_17R = 6 - FFMQpost_17_1,
    FFMQpost_19R = 6 - FFMQpost_19_1,
    FFMQpost_22R = 6 - FFMQpost_22_1,
    FFMQpost_23R = 6 - FFMQpost_23_1,
    FFMQpost_24R = 6 - FFMQpost_24_1,
    #create scales
    Desc_Ex_post =
        FFMQpost_1_1 + FFMQpost_2_1 + FFMQpost_5R + FFMQpost_11R + FFMQpost_16_1,
    Non_react_post = 
        FFMQpost_3_1 + FFMQpost_9_1 + FFMQpost_13_1 + FFMQpost_18_1 + FFMQpost_21_1,
    Observe_inner_post = 
        FFMQpost_6_1 + FFMQpost_10_1 + FFMQpost_15_1 + FFMQpost_20_1,
    Self_compasion_post = 
        FFMQpost_4R + FFMQpost_7R + FFMQpost_14R + FFMQpost_19R + FFMQpost_24R,
    Acting_mindful_post = 
        FFMQpost_8R + FFMQpost_12R + FFMQpost_17R + FFMQpost_22R + FFMQpost_23R,
    FFMQ_post_total = 
        Desc_Ex_post + Non_react_post + Observe_inner_post + Self_compasion_post + Acting_mindful_post
    )
Mothership <- left_join(Mothership,FMMQ_post, by = join_by(ID1 == ID1))

view(Mothership)
# df_5 <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_4250-4350.sav")
```

@@

```{r}
view(Mothership_post)
```

@@

Mothership_lasso <- Mothership_post |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  #!is.na(Anxiety_Responder),
  ) |>
  select( c(
    ID1,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, CUDOS_pre, CUDOS_post,
    #ACT stuff
    AAQIIpre, AAQIIpost, 
    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
    Acting_mindful_post, FFMQ_post_total, 
    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    Acting_mindful_pre, FFMQ_post_total
  ))
Mothership_lasso_1 <- na.omit(Mothership_lasso)

dim(Mothership_lasso_1)

@@

```{r}
### Anxeity 
Mothership_lasso_anx <- Mothership_post_anx |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  !is.na(Anxiety_Responder),
  CUXOS_pre >= 20,
  ) |>
  select( c(
    ID1,Anxiety_Responder,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC,
        #ACT stuff
    AAQIIpre, AAQIIpost, 
    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
    Acting_mindful_post, FFMQ_post_total, 
    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    Acting_mindful_pre, FFMQ_post_total
  ))
Mothership_lasso_anx <- na.omit(Mothership_lasso_anx)

### depression
Mothership_lasso_dep <- Mothership_post_dep |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Depression_Responder),
    CUDOS_pre >= 20,
  ) |>
  select( c(
    ID1, Depression_Responder,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC,
    #ACT stuff
    AAQIIpre, AAQIIpost, 
    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
    Acting_mindful_post, FFMQ_post_total, 
    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    Acting_mindful_pre, FFMQ_post_total

  ))
Mothership_lasso_dep <- na.omit(Mothership_lasso_dep)

@@

Vars_dep <- Mothership_lasso_dep |>
  select( c(
    Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, 
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, #Substance_D, #Psychotic_D,  
    Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
# Pre variables
    CUDOS_pre,CUXOS_pre,
    AAQIIpre,
    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre,
    Acting_mindful_pre,
  #post stuff    
     # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1,
    # RDQ
    # rdqPOST_coping:rdqPOST_wbs,
    #ACT stuff

    AAQIIpost,
    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
    Acting_mindful_post,

  ))

@@

```{r}
# # min model - old
# glm_min_dep <-
#           glm(
#     #Outcome varaible
#       Depression_Responder ~
#     # predictors
#       Age_1  + Some_College + Married + IPT_track_1 +
#       Days_complete_1 + Days_not_attended_1 + Anxiety_D + Trauma_D +
#       Trauma_C + Substance_C +
#       rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
#     #data
#       data = Vars_dep,
#     # type of regression : logistic = binary / binomial
#       family = "binomial",
#     )

# # min model - pre
# glm_min_dep <-
#           glm(
#     #Outcome varaible
#       Depression_Responder ~
#     # predictors
#       White  +   Anxiety_C + BPD_Co_C+  Current_Dx + CUXOS_pre + 
#       Self_compasion_pre,
#     #data
#       data = Vars_dep,
#     # type of regression : logistic = binary / binomial
#       family = "binomial",
#     )

# min model - pre/post
glm_min_dep <-
          glm(
    #Outcome varaible
      Depression_Responder ~
    # predictors
      White  +  Days_not_attended_1 + Anxiety_C + Current_Dx + CUXOS_pre +
      Non_react_post + AAQIIpost + Acting_mindful_post,
    #data
      data = Vars_dep,
    # type of regression : logistic = binary / binomial
      family = "binomial",
    )

# install.packages("rempsyc")

@@

# R^2 values  
  R2.min.dep <- performance::r2(glm_min_dep)
  R2.min.dep

  #wald
   library(aod)
   wald.test(b = coef(glm_min_dep),Sigma = vcov(glm_min_dep),Terms= 2:7)

# df for Forrest plots
FP.min.dep <- data.frame(cbind(
  Variable = tidy.summary.min.dep$term[2:length(tidy.summary.min.dep$term)],
  OR = OR.min.dep [2:length(OR.min.dep)],
  OR_low  = CI.min.dep [2:length(CI.min.dep$X2.5..),1],
  OR_high = CI.min.dep [2:length(CI.min.dep$X97.5..),2],
  p.values = p.values.min.dep $X2[2:length(p.values.min.dep$X2)]
                    ))

@@

Vars_anx <- Mothership_lasso_anx |>
  select( c(
    Anxiety_Responder,
    # Demographics
    Age_1,Some_College:Married,White, 
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, 
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    # rdqPOST_coping:rdqPOST_wbs,
        #ACT stuff
    AAQIIpre, AAQIIpost, 
    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
    Acting_mindful_post, 
    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    Acting_mindful_pre
  ))

@@

## min model
  glm_min_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
        Female + Married + White + Days_not_attended_1 + 
        Anxiety_D +  BPD_Co_C + CUXOS_pre +  
        AAQIIpost + Non_react_post + Self_compasion_post + Acting_mindful_post,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")

@@

#wald
   library(aod)
   wald.test(b = coef(glm_min_anx),Sigma = vcov(glm_min_anx),Terms= 2:12)

@@

#Change the names of variables
# FP_anx$Variable = c("Age", "Unmarried", "Days Completed", 
#                     "Days Not Attended", "Anixety Disorder","Trauma Disorder", 
#                     "Other Disorder", "Co-Mood Disorder",  "Co-BPD", 
#                     "Co-SUD", "CUXOS Pre", "Post Coping", 
#                     "Post PMH", "Post Functioning", "Post Wellbeing")

@@

FP_dep <- read_csv("~/Downloads/FP.min.dep")

@@

# FP_dep$Variable = c(
#                      "Days Not Attended",
#                     "Post Coping", 
#                     "Post PMH", "Post Functioning", "Post Wellbeing")
